Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-26 manuscript/manuscript.Rmd
mini
abstract

abstract: |
  Existing methods for optimal control struggle to deal with the
  complexity commonly encountered in real-world systems, including
  dimensionality, process error, model bias and data heterogeneity.
  Instead of tackling these system complexities directly, researchers 
  have typically sought to simplify models to fit optimal control 
  methods. But when is the optimal solution to an approximate, stylized 
  model better than an approximate solution to a more accurate model? 
  While this question has largely gone unanswered owing to the 
  difficulty of finding even approximate solutions for complex models, 
  recent algorithmic and computational advances in deep reinforcement 
  learning (DRL) might finally allow us to address these questions. DRL 
  methods have to date been applied primarily in the context of games 
  or robotic mechanics, which operate under precisely known rules. Here, 
  we demonstrate the ability for DRL algorithms using deep neural networks 
  to successfully approximate solutions (the ‘‘policy function’’ or control 
  rule) in a non-linear three-variable model for a fishery without knowing 
  or ever attempting to infer a model for the process itself. We find that 
  the reinforcement learning agent discovers an effective simplification of
  the problem to obtain an interpretable control rule. We show that the 
  policy obtained with DRL is both more profitable and more sustainable 
  than any constant mortality policy---the standard family of policies 
  considered in fishery management.

@@

In the main text we focused on the non-stationary model (‘‘three species, two fisheries, non-stationary’’ in Table 1) for the sake of space and because our results were most compelling there.
Here we present the reward distributions for the other models considered---the three stationary models, lines 1-3 in Table 1.

>>>>

abstract: |
  Existing methods for optimal control struggle to deal with the
  complexity commonly encountered in real-world systems, including
  dimensionality, process error, model bias and data heterogeneity.
  Instead of tackling these system complexities directly, researchers 
  have typically sought to simplify models to fit optimal control 
  methods. But when is the optimal solution to an approximate, stylized 
  model better than an approximate solution to a more accurate model? 
  While this question has largely gone unanswered owing to the 
  difficulty of finding even approximate solutions for complex models, 
  recent algorithmic and computational advances in deep reinforcement 
  learning (DRL) might finally allow us to address these questions. DRL 
  methods have to date been applied primarily in the context of games 
  or robotic mechanics, which operate under precisely known rules. Here, 
  we demonstrate the ability for DRL algorithms using deep neural networks 
  to successfully approximate solutions (the ‘‘policy function’’ or control 
  rule) in a non-linear three-variable model for a fishery without knowing 
  or ever attempting to infer a model for the process itself. We find that
  the reinforcement learning agent discovers a policy that outperforms both
  constant escapement and constant mortality policies---the standard family of policies 
  considered in fishery management. This DRL policy has 
  the shape of a constant escapement policy whose escapement values depend
  on the stock sizes of other species in the model.

@@

In the main text we focused on the non-stationary model (‘‘three species, two fisheries, non-stationary’’ in Table 1) for the sake of space and because our results were most compelling there.
Here we present the reward distributions for the other models considered---the three stationary models, lines 1-3 in Table 1.
These results are shown in Figs. \ref{fig:main_32}, \ref{fig:main_31} and \ref{fig:main_11}.
